Untitled

### 2024-01-30 Evalsims.Rmd
new

plt1 <- ggplot(out[out$bin == "marginal"], aes(x = shape, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(x = TeX("Distribution shift in training data ($\\kappa_{train}$)"), y = "Interval Width") +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank())) + 
 theme(legend.text = element_text(size = 11), legend.key.size = unit(2, "lines"))

plt1
ggsave("plots/calibration_shift.pdf" , width = 7, height = 5)

plt2 <- ggplot(out[out$bin == "marginal"], aes(x = shape, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(x = TeX("Distribution shift in training data ($\\kappa_{train}$)"), y = TeX("Coverage ($\\alpha = 0.1$)")) +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank())) + 
 theme(legend.text = element_text(size = 11), legend.key.size = unit(2, "lines"))

>>>>

out[,  shape_error := cal_error[method == "Uncond-CP" & bin == "marginal"], by = shape]

plt1 <- ggplot(out[out$bin == "marginal"], aes(x = shape_error, y = width, color = method)) + geom_point(aes(shape = method), size = 4)   + theme_bw() + labs(x = TeX("Calibration error in f( )"), y = "Interval Width") +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank())) + 
 theme(legend.text = element_text(size = 11), legend.key.size = unit(2, "lines"))

plt1
ggsave("plots/calibration_shift.pdf" , width = 6, height =4)

plt2 <- ggplot(out[out$bin == "marginal"], aes(x = shape, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(x = TeX("Calibration error in f()"),  y = TeX("Coverage ($\\alpha = 0.1$)")) +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank())) + 
 theme(legend.text = element_text(size = 11), legend.key.size = unit(2, "lines"))
